mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2023-01-13 rj/mathml.Rmd
add ref

The R\ extension of the markdown language [@Xie2020] enables reproducible
statistical reports with nice typesetting in HTML, Microsoft Word, and Latex.
Since recently [@R, version 4.2], R\'s manual pages include support for
mathematical expressions [@Sarkar2022], which already is a big improvement.
However, rules for the mapping of built-in language elements to their
mathematical representation are still lacking. So far, R\ expressions such
as `pbinom(k, N, p)` are printed as they are; pretty mathematical formulae
such as \(P_{\mathrm{Bi}}(X \le k; N, p)\) require explicit Latex commands, that
is, `P_{\mathrm{Bi}}\left(X \le k; N, p\right)`. Except for minimalistic use
cases, these commands are tedious to type in and their source code is hard to
read.

>>>>

The R\ extension of the markdown language [@Xie2020] enables reproducible
statistical reports with nice typesetting in HTML, Microsoft Word, and Latex.
Since recently [@R, version 4.2], R\'s manual pages include support for
mathematical expressions [@Sarkar2022;@Viechtbauer2022], which already is a big
improvement. However, rules for the mapping of built-in language elements to
their mathematical representation are still lacking. So far, R\ expressions such
as `pbinom(k, N, p)` are printed as they are; pretty mathematical formulae
such as \(P_{\mathrm{Bi}}(X \le k; N, p)\) require explicit Latex commands, that
is, `P_{\mathrm{Bi}}\left(X \le k; N, p\right)`. Except for minimalistic use
cases, these commands are tedious to type in and their source code is hard to
read.
